---
title: "Assignment 5"
author: "Adriana LH"
date: "10/6/2020"
output:
   html_document:
    theme: cosmo
    toc: true
    toc_depth: 3
    toc_float: true
    highlight: zenburn
---

```{r load libraries, include = FALSE}
library(tidyverse)
library(jtools)
library(interactions)
library(knitr)
library(tidycensus)
```

## Loading my data 
```{r}
vars <- c(hispanic_latino = "B03002_012", 
          white_alone = "B03002_003",
          black_alone = "B03002_004",
          asian_alone = "B03002_006",
          total_pop = "B01003_001", 
          internet_access = "B28002_001", 
          med_age = "B01002_001",
          foreign_born = "B05002_013")

MA_tracts <- get_acs(geography = "tract",
                     variables = vars,
                     state = "MA",
                     county = "Suffolk",
                     output = "wide")

MA_tracts <- MA_tracts %>%

  mutate(pct_latino = hispanic_latinoE/total_popE,
         pct_white = white_aloneE/total_popE,
         pct_black = black_aloneE/total_popE,
         pct_asian = asian_aloneE/total_popE,
         large_foreign = foreign_bornE/total_popE >0.25) %>%
  
  mutate(maj_race = case_when(pct_latino > 0.5 ~ "latino",
                              pct_white > 0.5 ~ "white",
                              pct_black > 0.5 ~ "black",
                              pct_asian > 0.5 ~ "asian",
                              TRUE ~ "1no_majority")) %>%
  
  mutate(internet_acc = internet_accessE/total_popE) %>%
  
  select(large_foreign, internet_acc, med_ageE, maj_race, total_popE)
```

## Loading my model
First I will load the regression model I used in Assignment 4, just for clarity and ease of referring back to. I've included all variables EXCEPT the total population of each tract in my model because I do not think that the total population of a census tract impacts a household's internet access.

```{r}
model1 <- lm(internet_acc ~ large_foreign + maj_race + med_ageE, 
            data = MA_tracts)

summary(model1)
```


## Second regression model with Log Transformation
For my second regression model, I will try to log transform the median age value and see if that strengthens model fit.

```{r}
model2 <- lm(internet_acc ~ large_foreign + maj_race + log(med_ageE), 
            data = MA_tracts)

summary(model2)
```

It looks like the R-squared value of model 2 is about 2 percentage points higher than model 1, so it's slightly better!

## Converting Age to a Categorical Variable

I'm wondering if results become clearer if I parse out age values in terms of life-stages. 
```{r}
MA_tracts <- MA_tracts %>% 
  mutate(age_range = case_when(med_ageE < 30 ~ "twenties",
                              med_ageE < 40 ~ "thirties",
                              med_ageE < 60 ~ "middle aged",
                              med_ageE < 80 ~ "senior"))

model3 <- lm(internet_acc ~ large_foreign + age_range + maj_race,
data = MA_tracts) 

summary(model3)
```

I see here that the multiple R-squared value improves, but the adjusted r-squared value actually decreases by a percent.

## Visualizing model fit

```{r}
ModelFit <- tibble(model = c(1, 2, 3),
                   R_square = c(summary(model1)$adj.r.squared,
                                summary(model2)$adj.r.squared,
                                summary(model3)$adj.r.squared))
                        

ggplot(ModelFit, aes(x = model, y = R_square)) +
  geom_line() +
  scale_x_continuous(name = "",
                   breaks = breaks <- seq(1, 3, by = 1),
                   labels = paste("Model", breaks)) +
  scale_y_continuous(name = "Adjusted R-squared value") +
  theme_bw()
```

Model 2 is the best fitting model for my data set. 

## Organizing and visualizing my model results 
```{r}
coeff_names <- c("Median Age of Tract" = "med_ageE",
                 "Median Age of Tract\n(log-transformed)" = "log(med_ageE)",
            "Majority Race Asian\n(compared to no majority race)" = "maj_raceasian",
            "Majority Race Black \n(compared to no majority race)" = "maj_raceblack",
            "Majority Race Latino\n(compared to no majority race)" = "maj_racelatino",
            "Majority Race White\n(compared to no majority race)" = "maj_racewhite",
             "Nativity Within Census Tract" = "large_foreignTRUE")
                 

export_summs(model1, model2,
             error_format = "(p = {p.value})",
             error_pos = "same",
             model.names = c("Initial Model", "Preferred Model"),
             coefs = coeff_names)
              
```

```{r}
coeff_plot <- c("Median Age of Tract" = "med_ageE",
                 "Median Age of Tract\n(log-transformed)" = "log(med_ageE)",
            "Majority Race Asian\n(compared to no majority race)" = "maj_raceasian",
            "Majority Race Black \n(compared to no majority race)" = "maj_raceblack",
            "Majority Race Latino\n(compared to no majority race)" = "maj_racelatino",
            "Majority Race White\n(compared to no majority race)" = "maj_racewhite",
             "Nativity Within Census Tract" = "large_foreignTRUE")
            
            plot_coefs(model2, 
           coefs = coeff_plot,
           plot.distributions = TRUE,
           rescale.distributions = TRUE) +
  scale_x_continuous(name = "Effect on Internet Access")
```

