---
title: "Assignment 3"
author: "Adriana LH"
date: "9/21/2020"
output: 
 html_document:
    theme: cosmo
    highlight: zenburn
---
```{r load libraries, include = FALSE}
library(tidyverse)
library(tidycensus)
library(ggplot2)
```

```{r include = FALSE}
vars <- c(hispanic_latino = "B03002_012", 
          white_alone = "B03002_003",
          black_alone = "B03002_004",
          asian_alone = "B03002_006",
          total_pop = "B01003_001", 
          internet_access = "B28002_001", 
          med_age = "B01002_001",
          foreign_born = "B05002_013")

MA_tracts <- get_acs(geography = "tract",
                     variables = vars,
                     state = "MA",
                     county = "Suffolk",
                     output = "wide")

MA_tracts <- MA_tracts %>%

  mutate(pct_latino = hispanic_latinoE/total_popE,
         pct_white = white_aloneE/total_popE,
         pct_black = black_aloneE/total_popE,
         pct_asian = asian_aloneE/total_popE,
         large_foreign = foreign_bornE/total_popE >0.25) %>%
  
  mutate(maj_race = case_when(pct_latino > 0.5 ~ "latino",
                              pct_white > 0.5 ~ "white",
                              pct_black > 0.5 ~ "black",
                              pct_asian > 0.5 ~ "asian",
                              TRUE ~ "no_majority")) %>%
  
  mutate(internet_acc = internet_accessE/total_popE) %>%
  
  select(large_foreign, internet_acc, med_ageE, maj_race, total_popE)
```

I am looking into internet access within the multiple census tracts of Suffolk County, MA. I am examining the relationship between internet access (percentage of people with internet in each tract), racial/ethnic makeup of each census tract, the total population of each census tract, nativity of residents of the tract, and the median age. 

## Relationship #1: two continuous variables in three tests

```{r}
correlation1 <- cor.test(MA_tracts$med_ageE, MA_tracts$total_popE)

correlation1
```

```{r}
correlation2 <- cor.test(MA_tracts$med_ageE, MA_tracts$internet_acc)

correlation2
```

```{r}
correlation3<- cor.test(MA_tracts$total_popE, MA_tracts$internet_acc)

correlation3
```

Looking at the summaries above, we can see that for all three correlation tests, there is a weak but still statistically significant correlation with a 95% confidence Level. The correlation between median age and internet access is positive, while the correlation for the other two is negative.

I'm interested in visualizing summary number 2, as it had the largest correlation value of the three.

```{r}
ggplot(MA_tracts, aes(x = med_ageE, y = internet_acc)) +
  geom_point(size = 0.5, alpha = 0.25, position = "jitter") +
  geom_smooth() +
  theme_minimal() +
  scale_x_continuous(name = "Median Age of Residents") +
  scale_y_continuous(name = "Percent with Internet", 
                     breaks = seq(0, .5, by = .1),
                     labels = paste("%", 
                                    prettyNum(seq(0, .5, by = .1),
                                              big.mark = ","))) 
  
```

This is interesting and actually makes a lot of sense when viewed as a graph. It seems that there's a definite upward trend in gaining internet access between ages 20-30, but then it generally stays around the same. Logically, that does make sense; I can imagine that people moving out of their parents' houses and gaining employment may affect this huge bump in the early to mid 20's. 

## Relationship #2, two categorical variables

```{r}
chi_sq <- chisq.test(MA_tracts$maj_race, MA_tracts$large_foreign == "TRUE")
chi_sq
```

```{r}
chi_sq$observed
```

```{r}
chi_sq$expected
```

## Relationship #3, categorical variable (3 or more levels) + continuous variables

```{r}
anova <- aov (med_ageE ~ maj_race, data = MA_tracts)
summary(anova)
```

```{r}
anova <- aov (internet_acc ~ maj_race, data = MA_tracts)
summary(anova)
```

```{r}
anova <- aov (total_popE ~ maj_race, data = MA_tracts)
summary(anova)
```

Difference Check:

```{r}
differences <- TukeyHSD(anova)

as_tibble(cbind(pair = row.names(differences$maj_race),
                differences$maj_race))
```
```{r}
ggplot(MA_tracts, aes(x = maj_race, y = internet_acc)) +
  geom_violin() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_x_discrete(name = "Majority Race") +
  scale_y_continuous(name = "Percent with Internet", 
                      breaks = seq(0, .5, by = .1),
                     labels = paste("%", 
                                    prettyNum(seq(0, .5, by = .1),
                                              big.mark = ","))) 
```

## Relationship #4, binary variable and continuous variables

```{r}
difference1 = t.test(med_ageE ~ large_foreign == "TRUE", 
                    data = MA_tracts)
difference1
```

```{r}
difference2 = t.test(total_popE ~ large_foreign == "TRUE", 
                    data = MA_tracts)
difference2
```

```{r}
difference3 = t.test(internet_acc ~ large_foreign == "TRUE", 
                    data = MA_tracts)
difference3
```

```{r}
ggplot(MA_tracts, aes(x = large_foreign, y = internet_acc)) +
  geom_violin() +
  theme_bw() +
  scale_x_discrete(name = "Born in the US, yes or no",
                   labels = c("No", "Yes")) +
   scale_y_continuous(name = "Percent with Internet", 
                    breaks = seq(0, .5, by = .1),
                     labels = paste("%", 
                                    prettyNum(seq(0, .5, by = .1),
                                              big.mark = ","))) 
```

