---
title: "Assignment 1"
author: "Adriana Lasso-Harrier"
date: "9/6/2020"
output: html_document
---

```{r load libraries, include = FALSE}
library(tidyverse)
library(tidycensus)
```

## Unit of Analysis

I focused on household-level data within the 2018 American Community Survey. My unit of analysis is therefore the 2018 ACS. I retrieved this information using the following code:
```{r}
hh_vars_2018 <- pums_variables %>%
  distinct(year, survey, var_code, 
           var_label, data_type, level) %>%
  filter(level == "housing", year == 2018, survey == "acs1")
```
## Definition of Variables

I decided to focus my analysis within Massachusetts.

I focused on the following 5 variables. I am interested in learning about a household's access to internet, as it relates to the language(s) spoken in the household, as well as the household size, income, and rent as a percentage of household income.

1. Access to internet(categorical).

2. Household language (categorical).

3. Family income (continuous)

4. Gross rent as a percentage of household income (continuous)

5. Number of people in family (continuous)

```{r person data, message=FALSE, include=TRUE, results='hide'}
int_access <- get_pums(variables = c("ACCESS", 
                                      "HHL", 
                                      "FINCP", 
                                      "NPF", 
                                      "GRPIP"),  
                       
                        state = "MA", 
                        year = 2018, 
                        survey = "acs1",
                        recode = TRUE) %>%
  filter(GRPIP > 0) %>%
  select(ACCESS_label, HHL_label, FINCP, NPF, GRPIP)
int_access<- int_access[int_access$ACCESS_label!= "N/A (GQ/vacant)",]
int_access<- int_access[int_access$HHL_label!= "N/A (GQ/vacant)",]
```
## Definition of Sample Population
As you can see from above, I filtered the dataset to include all gross rent percentages over 0. I also included two lines of code at the bottom that omitted any N/A respondents from the dataset, as there were about a thousand people who didn't answer either the internet access and/or the household language questions, and I wanted a complete dataset. 

## Number of Observations
My data set includes 17,573 observations of 5 variables. 

```{r}
head(int_access, n=10)
```

## Saved Dataset
My saved dataset is below.
```{r}
write_csv(int_access, "internet.csv")
```


