---
title: "Assignment 1"
author: "Adriana Lasso-Harrier"
date: "9/6/2020"
output: html_document
---

```{r load libraries, include = FALSE}
library(tidyverse)
library(tidycensus)
```

## Unit of Analysis

I focused on person-level data within the 2018 American Community Survey using the following code.
```{r}
person_vars_2018 <- pums_variables %>%
  distinct(year, survey, var_code, 
           var_label, data_type, level) %>%
  filter(level == "person", year == 2018, survey == "acs1")
```
## Definition of Variables

I decided to focus my analysis within Massachusetts.

I focused on six variables total (3 categorical and 3 numerical).

1. Access to internet(categorical).

2. Household language (categorical).

3. Means of transportation to work (categorical).

4. Income (numerical).

5. Age (numerical).

6. Travel time to work (numerical).

```{r person data, message=FALSE, include=TRUE, results='hide'}
int_access <- get_pums(variables = c("ACCESS", 
                                      "HHL", 
                                      "PINCP", 
                                      "AGEP", 
                                      "JWTR",
                                      "JWMNP"),
                        state = "MA", 
                        year = 2018, 
                        survey = "acs1",
                        recode = TRUE) %>%
  filter(AGEP > 18, JWMNP > 0) %>%
  select(ACCESS_label, HHL_label, JWTR_label, PINCP, AGEP, JWMNP)
int_access<- int_access[int_access$ACCESS_label!= "N/A (GQ/vacant)",]
int_access<- int_access[int_access$HHL_label!= "N/A (GQ/vacant)",]
```
## Definition of Sample Population
As you can see from above, I filtered by all respondents over the age of 18. I also made sure that travel time to work was greater than zero. I also included two lines of code at the bottom that ommitted any N/A respondents from the dataset, as there were about a thousand people who didn't answer either the internet access and/or the household language questions, and I wanted a complete dataset. 

## Number of Observations
My data set includes 31,732 observations of 6 variables. 

```{r}
head(int_access, n=10)
```

## Saved Dataset
My saved dataset is below.
```{r}
write_csv(int_access, "internet.csv")
```


